---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CMORplots

<!-- badges: start -->
<!-- badges: end -->

# Overview

The goal of **`plottools`** is to provide `ggplot2` themes and colour schemes for consistent figure formatting for CMOR outputs, and to provide additional geoms for use in constructing plots.

## Installation

You can install the latest version of CMORplots from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("uo-cmor/CMORplots")
```

## Example

**`plottools`** provides functions to extend [ggplot2](https://github.com/tidyverse/ggplot2) with a selection of colour palettes and plot themes to provide a consistent style for CMOR outputs.

### Colour palettes

`scale_colour_cmor()` and `scale_fill_cmor()` provide access to several selected colour palettes. All included colour palettes are colour-blind friendly.

```{r palettes}
library(ggplot2)
library(CMORplots)

# By default, scale_colour_cmor() uses the 'Color Universal Design' palette (https://jfly.uni-koeln.de/color/#pallet)
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_colour_cmor()

# This can be changed to an alternative colour scheme with the `palette` argument:
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_colour_cmor(palette = "Vibrant")
```

To get a list of the available colour palettes by name, use `list_cmor_colours()`, or generate a figure showing all available colours:

```{r plot-colours}
plot_cmor_colours()
```

### Themes

The only theme currently included is CMOR Classic, which simply replicates `theme_classic()` for now -- tweaking of this theme and addition of extra themes for specific use cases is planned.

```{r themes}
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  theme_cmor_classic()
```
